---
title: "ImmunoVax Immunosuppressive Medication Report"
format:
  html: 
    fontsize: 1.1em
    linestretch: 1.7
    tbl-colwidths: [1,1,1]
---

```{r}
#| echo: false
#| warning: false
source("R_functions/project_libraries.R")
source("R_functions/descriptive_Table_func.R")
```

```{r}
#| warning: false
#| echo: false


endterms <- c("CURRENTLY UNTREATED",  "NO TTT", "NO CANCER TTT", "REMISSION")
ongoingterms <- c("ONGOING", "CURRENTLY", "SINCE", "FROM", "TODAY", "UNTIL NOW", "DEPUIS")
dates <- paste(c( "\\d{1,2}\\.19\\d{2}|\\d{1,2}\\.20\\d{2}|19\\d{2}|20\\d{2}|\\d{2}\\.\\d{2}\\.\\d{2,}|(?!=\\.)\\d{2}\\.2\\d{1}(?!\\d{2})|(?!=\\.)\\d{2}\\.9\\d{1}(?!\\d{2})"  ), collapse="|")

data <- clean_names(read_csv("derived_data/ImmunoVax_ATCcodes.csv")) %>%
  group_by(ptid_4) %>%
  mutate(followup_st =min(as.Date(analysis_date, format= "%d/%b/%Y"))-60) %>%
   dplyr::select(1:4,22:30, 37:42) %>%
  mutate(imm_ther_mod = str_replace_all(immunosuppressive_therapy,
                                        c("Jan " = "01.",
                                          "FÉVrier " = "02.",
                                          "Mars " = "03.",
                                          "March " = "03.",
                                          "Mai " = "05.",
                                          "August " = "08.",
                                          "Novembre " = "11."
                                          ))) %>%
  mutate(last_trt = str_extract_all(imm_ther_mod, dates)) %>%

  unnest(cols= last_trt, keep_empty = TRUE) %>%
  mutate(last_trt = parse_date_time(last_trt, c("dmy", "mY", "my", "Y")) ) %>%
  group_by(ptid_4) %>%
  mutate(last_trt =max(last_trt)) %>%
  ungroup() %>%
  mutate(no_treat = case_when(grepl("No TTT", immunosuppressive_therapy) ~ 1,
                              !grepl("No TTT", immunosuppressive_therapy) ~ 0,
                              currently_treated == "No" ~ 1 ,
                              currently_treated != "No" ~ 0)) %>%
  mutate(currently_treated_new = case_when(
    currently_treated =="Yes"  & type_of_medication != "Hormonal therapy"~ "Yes",
     last_trt >= ymd(followup_st)-30 ~ "Yes",
    group == "Cancer treatment_Horm."  & ptgroup == "ONM" ~ "No",
     is.na(currently_treated) & grepl(paste(ongoingterms, collapse = "|"),toupper(immunosuppressive_therapy)) ~ "Yes",
     currently_treated == "No" & grepl(paste(endterms, collapse = "|"),toupper(immunosuppressive_therapy)) ~ "No",
    is.na(currently_treated) & grepl(paste(endterms, collapse = "|"),toupper(immunosuppressive_therapy)) ~ "No",
     currently_treated == "No" & is.na(immunosuppressive_therapy) ~ "No",
      last_trt < ymd(followup_st)-30 ~ "No",
    currently_treated == "No" & is.na(last_trt)  ~ "No" ,
    is.na(currently_treated) & ptgroup == "CTO"  ~ "Yes"
    #is.na(currently_treated) & last_trt < year(followup_st) &

  )) %>%
 #filter(is.na(currently_treated_new)) %>%
  unique()


```
Updated Treatment Classification Rules for Unknown Status

Free Text Classifiers | Updated Treatment Classification|
|:--|:-|
|"CURRENTLY UNTREATED" |  No                             |
| "NO TTT"             |  No                             |
| "REMISSION"          |  No                             |
| "ONGOING"            |  Yes                            |
| "CURRENTLY"          |  Yes                            |
| "SINCE"              |  Yes                            |
| "TODAY"              |  Yes                            |
| "UNTIL NOW"          |  Yes                            |
| last treatment date less than 60 days before first visit date    |  Yes |
| last treatment date more than 60 days before first visit date    |  No |
| last treatment date less than 30 days before first vaccine    |  Yes |
| last treatment date more than 30 days before first vaccine  |  No |
| Organ Transplant Group   |  Yes |
| Hormonotherapy medications | No |





```{r}
#| warning: false
#| echo: false
# summary(desc_table_bygroup(dfr = data,
#                       vars = c("currently_treated", "currently_treated_new"),
#                      namsvars = c("Original Treatment Classification", "New Treatment Classification"),
#                    group= "ptgroup",
#                    compareGroups=F,
#                    na.rm=F,
#                    digits=4))

grouptot <- paste("Total n=", length(unique(data$ptid_4)), sep="")
newnames <- data %>% group_by(ptgroup) %>%
  summarise( n= n(),  .groups = "keep") %>% 
  mutate(names = paste(ptgroup, " n=", n, sep = ""))

newnames <- as.vector(newnames$names)
newnames <- c(" ", "Currently Treated", newnames, grouptot)
tab<- summary(univariateTable(ptgroup~currently_treated+currently_treated_new,
                data=data,
currently_treated="Original Treatment Classification",
currently_treated_new="New Treatment Classification",

ptgroup.CTL="Controls",
ptgroup.CTO="Organ Transplant",
ptgroup.HEM="Haematology",
ptgroup.IAL="Immunodeficiency/ Systemic Inflammatory Disease",
ptgroup.ONM="Oncology",
compare.groups = FALSE))

knitr::kable(tab, digits = getOption("digits"), row.names = NA,
  col.names = c(paste(newnames)), caption = NULL, label = NULL,
  format.args = list(), escape = TRUE)
```




```{r}
#| warning: false
#| echo: false

CTOgroup <- data %>% filter(ptgroup == "CTO") 
```

```{r}
#| warning: false
#| echo: false

IALgroup <- data %>% filter(ptgroup == "IAL") 
```


```{r}
#| warning: false
#| echo: false

```

```{r}
#| warning: false
#| echo: false

HEMgroup <- data %>% filter(ptgroup == "HEM")   %>%
  mutate(L01A_alk_agents = case_when(grepl("L01A", atc_codelist)| grepl("L01A", ema_codelist)  ~ 1,
                                !grepl("L01A", atc_codelist)| !grepl("L01A", ema_codelist) ~ 0,
                                currently_treated == "No" ~ 0),
         L01B_anti_metab= case_when(grepl("L01B", atc_codelist)| grepl("L01B", ema_codelist)  ~ 1,
                                 !grepl("L01B", atc_codelist)| !grepl("L01B", ema_codelist) ~ 0,
                               currently_treated == "No" ~ 0),
          L01E_pk_inhib = case_when(currently_treated == "Yes" & 
                                 type_of_medication == "Tyrosine kinase inhibitor TKI"| 
                                 is.na(currently_treated) & 
                                 type_of_medication == "Tyrosine kinase inhibitor TKI" ~ 1,
                               grepl("L01E", atc_codelist) | grepl("L01E", ema_codelist) ~ 1,
                              !grepl("L01E", atc_codelist)| !grepl("L01E", ema_codelist) ~ 0,
                              grepl("CDK 4inhib", immunosuppressive_therapy) &
                                currently_treated == "Yes" | is.na(currently_treated) ~ 1,
                                currently_treated == "No" ~ 0),
         
         L01F_mono_antib = case_when(currently_treated == "Yes" &
                                  type_of_medication == "Anti-HER2 antibody therapy"|
                                  type_of_medication == "Antibody-drug conjugate" |
                                  type_of_medication == "VEGF inhibitor"   ~ 1,
                                is.na(currently_treated) & 
                                 type_of_medication == "Anti-HER2 antibody therapy"|
                                  type_of_medication == "Antibody-drug conjugate" |
                                  type_of_medication == "VEGF inhibitor"  ~ 1,
                                grepl("L01F", atc_codelist)| grepl("L01F", ema_codelist)  ~ 1,
                                !grepl("L01F", atc_codelist)| !grepl("L01F", ema_codelist) ~ 0,
                                currently_treated == "No" ~ 0),
          L01X_other_antineo = factor(case_when(currently_treated == "Yes" & 
                                 type_of_medication == "PARP inhibitor" ~ 1,
                               is.na(currently_treated) & 
                                 type_of_medication == "PARP inhibitor" ~ 1,
                               grepl("L01X", atc_codelist)|grepl("L01X", ema_codelist) ~ 1,
                              !grepl("L01X", atc_codelist)|!grepl("L01X", ema_codelist)~ 0,
                                currently_treated == "No" ~ 0), levels = c(0, 1)),
         L04A_immnosup = case_when( grepl("L04A", atc_codelist)|grepl("L04A", ema_codelist) ~ 1,
                              !grepl("L04A", atc_codelist)|!grepl("L04A", ema_codelist)~ 0,))

# univariateTable( disease ~ L01A_alk_agents +  
#                    L01E_pk_inhib + L01F_mono_antib + L01X_other_antineo  + L04A_immnosup,
#                  data = HEMgroup)
 # desc_table_bygroup(dfr = HEMgroup,
 #                      vars = c("no_treat", "L01A_alk_agents" ,  "L01E_pk_inhib" ,
 #                               "L01F_mono_antib" , "L01X_other_antineo" , "L04A_immnosup"),
 #                     namsvars = c("No Treatment", "L01A: Alkylating Agents", "L01E: Protein Kinase Inhibitors",
 #                                  "L01F: Monocloncal Antibodies", "L01X: Other Antineoplastics","L04A: Immunosuppressants"),
 #                   group= "disease",
 #                   compareGroups=F,
 #                   na.rm=F,
 #                   digits=4)  %>% 
 #  filter(Level != "Missing values" ) %>%
 #  mutate(Variable = case_when(Level != "n" & lag(Level,1)=="n" ~ lag(Variable, 1),
 #                              Level != "n" & lag(Level,2)=="n" ~ lag(Variable, 2))) %>%
 #  filter(Level != "n") %>%
 #  group_by(Variable) %>%
 #  arrange(Level, .by_group = TRUE) %>%
 #  mutate(Variable = ifelse(Level == "0", "", Variable))


  # filter(Level != "Missing values") %>%
  # arrange(Variable, Level)
# %>%
#   mutate(Variable = ifelse(Level == "1",lag(Variable, 2), Variable)) 
#%>%
  #filter(Level == "1" ) %>%
  #dplyr::select(-Level) 


```


```{r}
#| warning: false
#| echo: false
# desc_table_bygroup(dfr = HEMgroup,
#                       vars = c("no_treat", "L01A_alk_agents" ,  "L01E_pk_inhib" ,
#                                "L01F_mono_antib" , "L01X_other_antineo" , "L04A_immnosup"),
#                      namsvars = c("No Treatment", "L01A: Alkylating Agents", "L01E: Protein Kinase Inhibitors",
#                                   "L01F: Monocloncal Antibodies", "L01X: Other Antineoplastics","L04A: Immunosuppressants"),
#                    groupvar= "disease",
#                    compareGroups=F,
#                    na.rm=F,
#                    digits=4)  
```

```{r}
#| warning: false
#| echo: false

ONMgroup <- data %>% filter(ptgroup == "ONM")  %>%
  mutate(L01A_alk_agents = case_when(grepl("L01A", atc_codelist)| grepl("L01A", ema_codelist)  ~ 1,
                                !grepl("L01A", atc_codelist)| !grepl("L01A", ema_codelist) ~ 0,
                                currently_treated_new == "No" ~ 0),
         # L01B_anti_metab= case_when(grepl("L01B", atc_codelist)| grepl("L01B", ema_codelist)  ~ 1,
         #                        !grepl("L01B", atc_codelist)| !grepl("L01B", ema_codelist) ~ 0,
         #                        currently_treated_new == "No" ~ 0),
         L01C_plant_alk = case_when(grepl("L01C", atc_codelist)| grepl("L01C", ema_codelist)  ~ 1,
                                !grepl("L01C", atc_codelist)| !grepl("L01C", ema_codelist) ~ 0,
                                currently_treated_new == "No" ~ 0),
         L01D_cytotox_antib = case_when(grepl("L01D", atc_codelist)| grepl("L01D", ema_codelist) ~ 1,
                                !grepl("L01D", atc_codelist)| !grepl("L01D", ema_codelist) ~ 0,
                                currently_treated_new == "No" ~ 0),
         
          L01E_pk_inhib = case_when(currently_treated_new == "Yes" & 
                                 type_of_medication == "Tyrosine kinase inhibitor TKI"| 
                                 is.na(currently_treated) & 
                                 type_of_medication == "Tyrosine kinase inhibitor TKI" ~ 1,
                               grepl("L01E", atc_codelist) | grepl("L01E", ema_codelist) ~ 1,
                              !grepl("L01E", atc_codelist)| !grepl("L01E", ema_codelist) ~ 0,
                              grepl("CDK 4inhib", immunosuppressive_therapy) &
                                currently_treated_new == "Yes" | is.na(currently_treated) ~ 1,
                                currently_treated_new == "No" ~ 0),
         
         L01F_mono_antib = case_when(currently_treated_new == "Yes" &
                                  type_of_medication == "Anti-HER2 antibody therapy"|
                                  type_of_medication == "Antibody-drug conjugate" |
                                  type_of_medication == "VEGF inhibitor"   ~ 1,
                                grepl("L01F", atc_codelist)| grepl("L01F", ema_codelist)  ~ 1,
                                !grepl("L01F", atc_codelist)| !grepl("L01F", ema_codelist) ~ 0,
                                currently_treated_new == "No" ~ 0),
          L01X_other_antineo = case_when(currently_treated_new == "Yes" & 
                                 type_of_medication == "PARP inhibitor" ~ 1,
                               is.na(currently_treated) & 
                                 type_of_medication == "PARP inhibitor" ~ 1,
                               grepl("L01X", atc_codelist)|grepl("L01X", ema_codelist) ~ 1,
                              !grepl("L01X", atc_codelist)|!grepl("L01X", ema_codelist)~ 0,
                                currently_treated_new == "No" ~ 0),
         L02B_horm_antag = case_when( grepl("L02B", atc_codelist)|grepl("L02B", ema_codelist) ~ 1,
                              !grepl("L02B", atc_codelist)|!grepl("L02B", ema_codelist)~ 0,
                               currently_treated_new == "No" ~ 0),
         L02A_hormones = case_when( grepl("L02A", atc_codelist)|grepl("L02A", ema_codelist) ~ 1,
                              !grepl("L02A", atc_codelist)|!grepl("L02A", ema_codelist)~ 0,
                               currently_treated_new == "No" ~ 0),
         L04A_immsup = case_when( grepl("L04A", atc_codelist)|grepl("L04A", ema_codelist) ~ 1,
                              !grepl("L04A", atc_codelist)|!grepl("L04A", ema_codelist)~ 0,
                               currently_treated_new == "No" ~ 0)
         
        )



#table(ONMgroup$Disease, ONMgroup$mono_antib)
# univariateTable( ~disease,
#                 data = ONMgroup)
# univariateTable( ~ L01A_alk_agents +  L01C_plant_alk + L01D_cytotox_antib + 
#                   L01E_pk_inhib + L01F_mono_antib + L01X_other_antineo +
#                    L02B_horm_antag + L02A_hormones + no_treat,
#                 data = ONMgroup)

# desc_table_bygroup(dfr = ONMgroup,
#                       vars = c("no_treat", "L01A_alk_agents","L01C_plant_alk",
#                                "L01D_cytotox_antib", "L01E_pk_inhib" ,
#                                "L01F_mono_antib" , "L01X_other_antineo",
#                                "L02B_horm_antag", "L02A_hormones", "L04A_immsup"),
#                      namsvars = c("No Treatment", "L01A: Alkylating Agents", "L01C: Plant Alkyloids", "L01D: Cytotoxic Antibiotics", "L01E: Protein Kinase Inhibitors", "L01F: Monocloncal Antibodies", "L01X: Other Antineoplastics", "L02B: Hormone Anatagonists", 
#                                   "L02A: Hormones", "L04A: Immunosuppressants"),
#                    group= "disease",
#                    compareGroups=F,
#                    na.rm=F,
#                    digits=4) %>%
#   mutate(Variable = lag(Variable, 2)) %>%
#   filter(Level == "1" ) %>%
#   dplyr::select(-Level)



```

Antibody Response Differences in Treated vs Untreated Immunocompromised Patients (No Controls)
during first 6 months of follow up 
```{r}
#| warning: false
#| echo: false
vax_resp_data <- clean_names(read_csv("derived_data/ImmunoVax_ATCcodes.csv")) %>%
  group_by(ptid_4) %>%
  mutate(visitct_ = as.numeric(factor(visit_time_point, levels=unique(visit_time_point)))) %>%
   filter(visitct_ == 1 & visit_time_point == "V3" |
           visitct_ == 2 & visit_time_point == "V4"|
           visitct_ == 3 & visit_time_point == "V5") %>%
  filter(is.na(days_since_1st_infection) | as.numeric(days_since_1st_infection) < as.numeric(days_since_2nd_dose )) 





meddata <- data %>%
  dplyr::select(c(1, 19:23))


vax_resp_data <- left_join(vax_resp_data, meddata, by = "ptid_4")  %>%
  filter(!is.na(currently_treated_new)) %>% 
  filter(ptgroup != "CTL") %>%
  mutate(anal_date = as.Date(analysis_date, format= "%d/%b/%Y"),
          med_cutoff = ymd(last_trt)+30) %>%
    # mutate(TKI = case_when(grepl("L01E", atc_codelist) & currently_treated_new == "Yes" ~ "Yes",
    #                        grepl("L01E", ema_codelist) & currently_treated_new == "Yes" ~ "Yes",
    #                      grepl("L01E", ema_codelist) & currently_treated_new == "No" ~ "No",
    #                      grepl("L01E", atc_codelist) & currently_treated_new == "No" ~ "No",
    #                     !grepl("L01E", ema_codelist) | !grepl("L01E", atc_codelist)~ "No",
    #                      is.na(ema_codelist) | is.na(atc_codelist)~ "No")) 
  mutate(TKI = case_when(type_of_medication == "Tyrosine kinase inhibitor TKI" & currently_treated_new == "Yes" ~ "Yes",
                         type_of_medication == "Tyrosine kinase inhibitor TKI" & currently_treated_new == "No" ~ "No",
                         type_of_medication != "Tyrosine kinase inhibitor TKI" ~ "No",
                         is.na(type_of_medication) ~ "No")) %>%
    mutate(JKI = case_when(type_of_medication == "Janus kinase inhibitors" & currently_treated_new == "Yes" ~ "Yes",
                         type_of_medication == "Janus kinase inhibitors" & currently_treated_new == "No" ~ "No",
                         type_of_medication != "Janus kinase inhibitors" ~ "No",
                         is.na(type_of_medication) ~ "No")) %>%
      mutate(imm_mod= case_when(type_of_medication == "Immunomodulator drugs IMIDs" & currently_treated_new == "Yes" ~ "Yes",
                         type_of_medication == "Immunomodulator drugs IMIDs" & currently_treated_new == "No" ~ "No",
                         type_of_medication != "Immunomodulator drugs IMIDs" ~ "No",
                         is.na(type_of_medication) ~ "No")) #%>%
      # mutate(vegf= case_when(grepl("Beva", immunosuppressive_therapy) & currently_treated_new == "Yes" ~ "Yes",
      #                    currently_treated_new == "No" ~ "No",
      #                   !grepl("Beva", immunosuppressive_therapy)  ~ "No")) 
      # 
  # mutate(currently_treated_new = case_when(is.na(last_trt) ~ currently_treated_new,
  #                                          anal_date  >= med_cutoff ~ "No", 
  #                                          anal_date  < med_cutoff ~ "Yes"
  #                                       ))

test <- vax_resp_data %>% filter(cov2nw > 1000)

t.test(vax_resp_data$cov2nw ~ vax_resp_data$TKI)
t.test(vax_resp_data$cov2nw ~ vax_resp_data$JKI)
t.test(vax_resp_data$cov2nw ~ vax_resp_data$imm_mod)
#t.test(vax_resp_data$cov2nw ~ vax_resp_data$vegf)

ttest_cov2nw  <- as.data.frame(cbind(t.test(vax_resp_data$cov2nw ~ vax_resp_data$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Wild Type", " "))

ttest_cov2no  <- as.data.frame(cbind(t.test(vax_resp_data$cov2no ~ vax_resp_data$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Omicron", " "))

ttest_cov2nd  <- as.data.frame(cbind(t.test(vax_resp_data$cov2nd ~ vax_resp_data$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Delta", " "))

tab<- rbind(ttest_cov2nw, ttest_cov2nd, ttest_cov2no) %>% mutate(temp = ifelse(rowname== "estimate", V1, "")) %>%
  filter(rowname == "p.value" | rowname == "estimate") %>%
  separate(temp, into= c("Unt", "Tr"),  sep = ",") %>%
  mutate(
         Untreated = ifelse(rowname != "p.value", parse_number(Unt), " "),
         Treated = ifelse(rowname != "p.value", parse_number(Tr), " "),
         p.value = ifelse(rowname == "p.value", V1, " ")) %>%
  dplyr::select(3,6:8) %>%
  mutate(Untreated = ifelse(as.character(round(as.numeric(Untreated), digits = 2)) == "NA", " ",as.character(round(as.numeric(Untreated), digits = 2))) ,
         Treated = round(as.numeric(Treated), digits = 2))


knitr::kable(tab, digits = 3, row.names = NA,
  col.names = NA , caption = NULL, label = NULL,
  format.args = list(), escape = TRUE)

```


```{r}
#| warning: false
#| echo: false

onmtest <- vax_resp_data %>%
  filter(ptgroup == "ONM") 


ttest_cov2nw  <- as.data.frame(cbind(t.test(onmtest$cov2nw ~ onmtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Wild Type", " "))

ttest_cov2no  <- as.data.frame(cbind(t.test(onmtest$cov2no ~ onmtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Omicron", " "))

ttest_cov2nd  <- as.data.frame(cbind(t.test(onmtest$cov2nd ~ onmtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Delta", " "))

tab<- rbind(ttest_cov2nw, ttest_cov2nd, ttest_cov2no) %>% mutate(temp = ifelse(rowname== "estimate", V1, "")) %>%
  filter(rowname == "p.value" | rowname == "estimate") %>%
  separate(temp, into= c("Unt", "Tr"),  sep = ",") %>%
  mutate(
         Untreated = ifelse(rowname != "p.value", parse_number(Unt), " "),
         Treated = ifelse(rowname != "p.value", parse_number(Tr), " "),
         p.value = ifelse(rowname == "p.value", V1, " ")) %>%
  dplyr::select(3,6:8) 


# knitr::kable(tab, digits = 3, row.names = NA,
#   col.names = NA , caption = NULL, label = NULL,
#   format.args = list(), escape = TRUE)
```



```{r}
#| warning: false
#| echo: false

ialtest <- vax_resp_data %>%
  filter(ptgroup == "HEM") 


ttest_cov2nw  <- as.data.frame(cbind(t.test(ialtest$cov2nw ~ ialtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Wild Type", " "))

ttest_cov2no  <- as.data.frame(cbind(t.test(ialtest$cov2no ~ ialtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Omicron", " "))

ttest_cov2nd  <- as.data.frame(cbind(t.test(ialtest$cov2nd ~ ialtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Delta", " "))

tab<- rbind(ttest_cov2nw, ttest_cov2nd, ttest_cov2no) %>% mutate(temp = ifelse(rowname== "estimate", V1, "")) %>%
  filter(rowname == "p.value" | rowname == "estimate") %>%
  separate(temp, into= c("Unt", "Tr"),  sep = ",") %>%
  mutate(
         Untreated = ifelse(rowname != "p.value", parse_number(Unt), " "),
         Treated = ifelse(rowname != "p.value", parse_number(Tr), " "),
         p.value = ifelse(rowname == "p.value", V1, " ")) %>%
  dplyr::select(3,6:8) 

```



```{r}
#| warning: false
#| echo: false

hemtest <- vax_resp_data %>%
  filter(ptgroup == "HEM") 


ttest_cov2nw  <- as.data.frame(cbind(t.test(ialtest$cov2nw ~ ialtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Wild Type", " "))

ttest_cov2no  <- as.data.frame(cbind(t.test(ialtest$cov2no ~ ialtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Omicron", " "))

ttest_cov2nd  <- as.data.frame(cbind(t.test(ialtest$cov2nd ~ ialtest$currently_treated_new))) %>% 
  rownames_to_column() %>% 
  mutate(Antibody= ifelse(rowname == "p.value", "Delta", " "))

tab<- rbind(ttest_cov2nw, ttest_cov2nd, ttest_cov2no) %>% mutate(temp = ifelse(rowname== "estimate", V1, "")) %>%
  filter(rowname == "p.value" | rowname == "estimate") %>%
  separate(temp, into= c("Unt", "Tr"),  sep = ",") %>%
  mutate(
         Untreated = ifelse(rowname != "p.value", parse_number(Unt), " "),
         Treated = ifelse(rowname != "p.value", parse_number(Tr), " "),
         p.value = ifelse(rowname == "p.value", V1, " ")) %>%
  dplyr::select(3,6:8) 

```

```{r}
#| warning: false
#| echo: false

# library(glmmTMB)
# library(DHARMa)
library(lme4)
library(car)

 # vax_resp_data <- vax_resp_data %>%
 #   mutate(response = ifelse(cov2nw<1, 1, cov2nw)) %>%
 #     mutate(response = ifelse(cov2nw>2430, 2430, cov2nw)) %>% filter(!is.na(days_since_2nd_dose))

 vax_resp_data <- vax_resp_data %>%
   mutate(response = ifelse(cov2nw<1, 1, cov2nw)) %>%
     mutate(response = ifelse(cov2nw>2000, 2000, cov2nw)) %>% filter(!is.na(days_since_2nd_dose))

 
 ggplot(vax_resp_data, aes(x = response)) + geom_density() + facet_wrap(currently_treated_new~ptgroup)
#anova(lm(response ~ visit_time_point +  currently_treated_new +  ptgroup , data = vax_resp_data))


 
 
model = lmer(response ~ days_since_2nd_dose +  currently_treated_new  + (1|ptgroup) + (1|ptid_4), data = vax_resp_data)

plot(model)


summary(model)
Anova(model, test="F")
confint(model)

vax_resp_data$fit <- predict(model)

library(ggplot2)
# ggplot(vax_resp_data,aes(days_since_2nd_dose, response, col=ptgroup, group=interaction(group,ptid_4), shape=currently_treated_new)) + 
#     geom_line(aes(y=fit), size=0.1)  +
#     #geom_hline(yintercept=0, linetype="dashed") +
#     tiale_bw()  + facet_grid(~currently_treated_new) 

ggplot(vax_resp_data,aes(days_since_2nd_dose, response, col=currently_treated_new, group=interaction(ptid_4))) + 
    geom_line(aes(y=fit), size=0.1)  +
  geom_point(size=0.2) +
    #geom_hline(yintercept=0, linetype="dashed") +
    theme_bw() 
# model_splines<- glmmTMB(response ~ days_since_2nd_dose +  currently_treated_new +  (1|ptid_4) + (1|ptgroup),
#                         data = vax_resp_data,
#                         family=Gamma)
# 
# #diagnose(model_splines) 
# summary(model_splines) 
# # AIC 
# 
# simulationOutput <- simulateResiduals(fittedModel = model_splines, n = 1000)
# plot(simulationOutput, quantreg=T)
#KS test: 
#dispersion test: 
#outlier test: 
#residuals: quantiles deviation detected

 
model2 = lmer(response ~ days_since_2nd_dose +  currently_treated_new  + (1|ptid_4) , data = vax_resp_data)




summary(model2)
Anova(model2, test="F")
confint(model2)

plot(model2)

vax_resp_data$fit2 <- predict(model2)

ggplot(vax_resp_data,aes(days_since_2nd_dose, response, col=currently_treated_new, group=interaction(ptid_4))) + 
    geom_line(aes(y=fit2), size=0.1)  +
  geom_point(size=0.2) +
    theme_bw() 




# 
# model3 = lmer(response ~ days_since_2nd_dose +  (1|currently_treated_new)  + (1|ptid_4) , data = vax_resp_data)
# 
# 
# 
# 
# summary(model3)
# Anova(model3, test="F")
# confint(model3)
# 
# vax_resp_data$fit3 <- predict(model3)
# 
# ggplot(vax_resp_data,aes(days_since_2nd_dose, response, col=currently_treated_new, group=interaction(ptid_4))) + 
#     geom_line(aes(y=fit3), size=0.1)  +
#   geom_point(size=0.2) +
#     theme_bw() 
```
